### 2020-07-01 docs/LaTex/Paper.tex
Minor fixes

\clearpage{\pagestyle{empty}\cleardoublepage}\pagestyle{empty}

\tableofcontents\cleardoublepage\pagestyle{myfancy} % set the pagestyle as empty for all toc pages

\newpage\thispagestyle{plain}\pagenumbering{arabic}% Arabic page numbers (and reset to 1)
\phantomsection\section*{Resumen}
Este documento proporciona una descripción detallada del proyecto, el cual está centrado en la investigación de posibles alternativas de bajo coste para sistemas de dendrometría inalámbricos. Actualmente existen una amplia gama de sistemas profesionales en el mercado, sin embargo debido a su elevado coste, este proyecto pretende abordar la reducción en el mismo, incrementando la versatilidad, accesibilidad y escalabilidad de este tipo de sistemas.

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\thispagestyle{plain}
\section{System Architecture}
A simple block diagram is shown in figure \ref{fig:block_diagram}, this diagram intends to emphasize the difference between two big layers, a physical layer that should be placed ---IoT dendrometers at least--- close to the sample, and another one called abstract layer which can be deployed locally ---TTN stack is a cloud server, although.

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\thispagestyle{plain}
\section{Design}\thispagestyle{plain}
Like in the Introduction, the most proper way to present this technical description is to difference between software and hardware parts. However, is still interesting to present a simple and general diagram for whole designed solution. So as the reader can see in the figure \ref{fig:GenView} is shown the general diagram.

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\thispagestyle{plain}
\section{Proof of concept}
\doubt{COMPLETE}

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\pagestyle{plain}
\section{Conclusions}
Finally there are a few considerations that could be done,

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\pagestyle{myfancy}
\phantomsection\addcontentsline{toc}{section}{References}
\printbibliography
\end{document}

>>>>

\clearpage{\pagestyle{empty}\cleardoublepage}\pagestyle{empty} % Forces the next section to start in an odd page.
\tableofcontents\cleardoublepage\pagestyle{myfancy} % set the pagestyle as empty for all toc pages

\clearpage{\pagestyle{empty}\cleardoublepage}\thispagestyle{plain} % Forces the next section to start in an odd page.
\pagenumbering{arabic}% Arabic page numbers (and reset to 1)
\phantomsection\section*{Resumen}
Este documento proporciona una descripción detallada del proyecto, el cual está centrado en la investigación de posibles alternativas de bajo coste para sistemas de dendrometría inalámbricos. Actualmente existen una amplia gama de sistemas profesionales en el mercado, sin embargo debido a su elevado coste, este proyecto pretende abordar la reducción en el mismo, incrementando la versatilidad, accesibilidad y escalabilidad de este tipo de sistemas.

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\thispagestyle{plain} % Forces the next section to start in an odd page.
\section{System Architecture}
A simple block diagram is shown in figure \ref{fig:block_diagram}, this diagram intends to emphasize the difference between two big layers, a physical layer that should be placed ---IoT dendrometers at least--- close to the sample, and another one called abstract layer which can be deployed locally ---TTN stack is a cloud server, although.

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\thispagestyle{plain} % Forces the next section to start in an odd page.
\section{Design}\thispagestyle{plain}
Like in the Introduction, the most proper way to present this technical description is to difference between software and hardware parts. However, is still interesting to present a simple and general diagram for whole designed solution. So as the reader can see in the figure \ref{fig:GenView} is shown the general diagram.

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\thispagestyle{plain}  % Forces the next section to start in an odd page.
\section{Proof of concept}
\doubt{COMPLETE}

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\pagestyle{plain}  % Forces the next section to start in an odd page.
\section{Conclusions}
Finally there are a few considerations that could be done,

@@

\clearpage{\pagestyle{empty}\cleardoublepage}\pagestyle{myfancy} % Forces the next section to start in an odd page.
\phantomsection\addcontentsline{toc}{section}{References}
\printbibliography
\end{document}
